Sequence Labeling for Gait Analysis using LSTM

### 2015-05-09 paper/paper.tex
Fixed fig placement
Signed-off-by: pabloi <itu.pablo@gmail.com>

\begin{figure}[H]
 \centering
 \includegraphics[scale=.45]{./figures/Test1_2Train1_1Compare.png}
 % \includesvg[scale=.31]{./figures/Test1_1Train1_2Compare.svg}
 % Test1_1Train1_2Compare.png: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=
 \caption{Comparison of Miller vs. LSTM network for various training intervals, for dataset 1.}
 \label{fig:halfAndHalfTrials}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[scale=.45]{./figures/Test2_1Train2_2Compare.png}
  %\includesvg[scale=.4]{./figures/Test2_2Train2_1Compare.svg}
 % Test1_1Train1_2Compare.png: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=
 \caption{Comparison of Miller vs. LSTM network for various training intervals, for dataset 2.}
 \label{fig:halfAndHalfUsers}
\end{figure}

@@

\subsection{Future work}
Although our results are promising and seem to improve the current state-of-the-art, there a few things that still can be done to assess and improve performance:
\begin{enumerate}
 \item Run a true grid search to find the best training parameters.
 \item Run the training for a longer time and use cross-validation to determine reasonable stopping criteria and avoid over-fitting.
 \item Use the network with a delay in the output, so we effectively use information of a window of time around the desired time sample to infer events. This would make this method more comparable to the exisiting algorithms, which usually work with the smoothing problem, and not with the real-time filtering problem. Arguably this could only improve the performance of the method, as more information would be available to make the classification of each sample.
 \item Assess generalization to pathological gait subjects.
 \item Assess generalization to over-ground walking data (no ground truth in our dataset).
 \item Investigate possible pre-processing to guarantee that method is invariant to walking speed, and subject height and weight.
 \item Study possible modifications to make the network truly invariant to the left/right symmetry. Currently the network is trained to output events for both legs with marker data from both sides of the body, but we know that the symmetry of the problem could be exploited further. However, this could prove to be an issue on subjects with highly asymmetrical gait.
 \item Incorporate prior information from the transitions that occurr during gait. In normal walking the events happen in a pre-established order (left heel-strike - right toe-off - right heel-strike - left toe-off) which gives us some information on the possible upcoming transitions based on the current state. While we can speculate that a recursive NN learns this with training, we could incorporate this information for better accuracy during normal walking conditions.
 \item Reduce the number of markers used to achive performance. While ours is a rich dataset, not all captures of motion data will include all the markers used. Furthermore we can expect the feet markers to contain the most information about the events.
\end{enumerate}

>>>>

\begin{figure}
 \centering
 \includegraphics[scale=.45]{./figures/Test1_2Train1_1Compare.png}
 % \includesvg[scale=.31]{./figures/Test1_1Train1_2Compare.svg}
 % Test1_1Train1_2Compare.png: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=
 \caption{Comparison of Miller vs. LSTM network for various training intervals, for dataset 1.}
 \label{fig:halfAndHalfTrials}
\end{figure}

@@

\begin{figure}
 \centering
 \includegraphics[scale=.45]{./figures/Test2_1Train2_2Compare.png}
  %\includesvg[scale=.4]{./figures/Test2_2Train2_1Compare.svg}
 % Test1_1Train1_2Compare.png: 0x0 pixel, 300dpi, 0.00x0.00 cm, bb=
 \caption{Comparison of Miller vs. LSTM network for various training intervals, for dataset 2.}
 \label{fig:halfAndHalfUsers}
\end{figure}

@@

\subsection{Future work}
Although our results are promising and seem to improve the current state-of-the-art, there a few things that still can be done to assess and improve performance:
\begin{enumerate}
 \item Run a true grid search to find the best training parameters.
 \item Run the training for a longer time and use cross-validation to determine reasonable stopping criteria and avoid over-fitting.
 \item Use the network with a delay in the output, so we effectively use information of a window of time around the desired time sample to infer events. This would make this method more comparable to the exisiting algorithms, which usually work with the smoothing problem, and not with the real-time filtering problem. Arguably this could only improve the performance of the method, as more information would be available to make the classification of each sample.
 \item Assess generalization to pathological gait subjects.
 \item Assess generalization to over-ground walking data (no ground truth in our dataset).
 \item Investigate possible pre-processing to guarantee that method is invariant to walking speed, and subject height and weight.
 \item Study possible modifications to make the network truly invariant to the left/right symmetry. Currently the network is trained to output events for both legs with marker data from both sides of the body, but we know that the symmetry of the problem could be exploited further. However, this could prove to be an issue on subjects with highly asymmetrical gait.
 \item Incorporate prior information from the transitions that occurr during gait. In normal walking the events happen in a pre-established order (left heel-strike - right toe-off - right heel-strike - left toe-off) which gives us some information on the possible upcoming transitions based on the current state. While we can speculate that a recursive NN learns this with training, we could incorporate this information for better accuracy during normal walking conditions.
 \item Reduce the number of markers used to achive performance. While ours is a rich dataset, not all  motion-capture datasets will include all the markers used. Furthermore we can expect the feet markers to contain the most information about the events, while other markers may be more easily discarded.
\end{enumerate}
